---
title: "cdpo1"
author: "Lukang Huang"
date: "2017Äê10ÔÂ15ÈÕ"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Package Description

We have Data matrix X and response data vector Y,We have a losso expression, we want to compute the parameter $\beta$.

First,we choose the penality parameter $\lambda$.

Second, we standarized the $X$ and $Y$.

Last, we use this package to get $\beta$ accroding to the coordinate descent and proximal operator algorithm.

## Simulation result

###Standarize the $X$ and $Y$





```{r pr}
n = 100
p = 500
sigma_noise = 0.05
beta = rep(0,p)
beta[1:6] = c(5,10,3,80,90,10)


XData = matrix(rnorm(n*p,sd=10),nrow=n,ncol=p)


#standarize the data
for(i in 1:500){
  X.sum <- sum(XData[,i]);
  for(j in 1:100){
    XData[j,i] <- XData[j,i] - X.sum/100
  }
  X.var <- sum((XData[,i]^2))
  for(j in 1:100){
    XData[j,i] <- 10*XData[j,i]/sqrt(X.var)
  }
}
YData = XData %*% beta + rnorm(n, sd = sigma_noise)
```

###Using the standarized data to run the code

```{r p}
#Using the standarized data to run the code
library(cdpo)
betahat1 <- cdLasso(YData,XData,0.33)$beta
betahat1[1:10]
diff1 <- betahat1 - beta



betahat2<-poLasso(YData, XData, 0.25)$beta
betahat2[1:10]

cdvalues<- cdLasso(YData,XData,0.33)$Functionvalue
cdvalues<-log10(cdvalues)
povalues<-poLasso(YData, XData, 0.25)$Functionvalue
povalues<-log10(povalues)


plot(cdvalues,xlim=c(0,1500),ylim=c(0,4),lwd=0.01,col='red',xlab="Iterate times",ylab="functionvalue",cex=0.1)
points(povalues,col='green',cex=0.1)
legend("bottomright",legend=c("cdLasso","poLasso"),col=c("red","green"),lty=1)
```


From the plot, we know coordinate descent algorithm has a faster speed to convergence, but proximal operator algorithm get a smaller lasso function value.
